Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-30 paper_v1.Rnw
Table 1 missing column values added

\begin{table*}[th]
\label{tab:s1sum}
\caption{Summary statistics of learner demographics and behavior in 14 MOOCs}
\small
\center
\begin{tabular}{llccccccccccc}
% & & & & & & & & $>$ 30\% & $>$ 50\% & $>$ 80\% & Self-Rep. \\
% & Topic Area & Enrollment & Course survey & Feedback survey & Female & Age & Education & videos & videos & videos & Dropout \\
\toprule
 &            &          & \multicolumn{3}{c}{Survey Responses} & & & & & \multicolumn{3}{c}{Videos Watched} \\
 \cmidrule(r){4-6} \cmidrule(r){11-13}
 & Topic Area & Enrolled & Initial & Feedback & Both & Female & Age$^1$   & Education$^2$ & Dropout$^3$ & $>$ 30\% & $>$ 50\% & $>$ 80\% \\
\midrule
C1 & Business & 61,096   & 9,943  & 2,367    & N    & 42\%   & 39 (30,49) & n.a.       & 10\% & 39\% & 20\% & 7\% \\
C2 & Business & 41,081   & 6,544  & 883      & N    & 40\%   & 39 (30,49) & 97\%       & 9\%  & 32\% & 13\% & 2\% \\
C3 & CS       & 27,104   & 6,104 & 2,854     & N    & 35\%   & 30 (22,41) & 74\%       & 2\%  & 67\% & 40\% & 7\% \\
C4 & CS       & 56,154   & 3,406 & 1,123     & N    & 11\%   & 33 (27,42) & 91\%       & 21\% & 34\% & 16\% & 11\% \\
C5 & CS       & 57,636   & 5738  & 402       & N    & 17\%   & 33 (26,43) & 91\%       & 14\% & 66\% & 55\% & 28\% \\
C6 & Engineering & 16,220 & 2,540 & 269      & N    & 13\%   & 33 (27,45) & 92\%       & 15\% & 62\% & 49\% & 17\% \\
C7 & Enginerring & 7,178 & 1,312 & 202       & N    & 12\%   & 27 (22,39) & 85\%       & 7\%  & 51\% & 18\% & 2\% \\
C8 & Humanities & 7,634 & 3,631  & 152       & N    & 92\%   & 33 (26,45) & 93\%       & 7\%  & 45\% & 11\% & 0\% \\
C9 & Humanities & 6,475 & 3,315  & 326       & N    & 90\%   & 32 (27,47) & 91\%       & 16\% & 69\% & 50\% & 17\% \\
C10 & Humanities & 9,903 & 4,227 & 1,570     & N    & 52\%   & 39 (29,52) & 89\%       & 3\%  & 84\% & 74\% & 21\% \\
C11 & Humanities & 630 & 167     & 80        & N    & 50\%   & 30 (27,40) & 97\%       & 16\% & 74\% & 55\% & 16\% \\
C12 & Math \& Stats & 49,317 & 3,090 & 862   & N    & 33\%   & 41 (29,55) & 88\%       & 31\% & 27\% & 10\% & 1\% \\
C13 & Math \& Stats & 32,006 & 26,142 & 5,336 & N   & 58\%   & 28 (16,46) & n.a.       & 4\%  & 69\% & 38\% & 8\% \\
C14 & Math \& Stats & 16,857 & 2,892 & 363   & N    & 9\%    & 31 (26,38) & 99\%       & 14\% & 61\% & 45\% & 25\% \\
C15 & Math \& Stats & 37,017 & 11,629 & 1,854 & N   & 20\%   & 35 (29,45) & 98\%       & 8\%  & 78\% & 67\% & 34\% \\
C16 & Math \& Stats & 27,236 & 2,711 & 637   & N    & 82\%   & 43 (34,51) & n.a.       & 1\%  & 64\% & 36\% & 5\% \\
C17 & Math \& Stats & 13,132 & 3,629 & 843   & N    & n.a.   & n.a.       & n.a.       & 5\%  & 70\% & 54\% & 14\% \\
\bottomrule
\multicolumn{13}{l}{$^1$ mean (upper, lower quartile)  $^2$ bachelors' or higher degree  $^3$ self-reported in the feedback survey}
\end{tabular}
\end{table*}

>>>>

\begin{table*}[th]
\label{tab:s1sum}
\caption{Summary statistics of learner demographics and behavior in 14 MOOCs}
\small
\center
\begin{tabular}{llccccccccccc}
% & & & & & & & & $>$ 30\% & $>$ 50\% & $>$ 80\% & Self-Rep. \\
% & Topic Area & Enrollment & Course survey & Feedback survey & Female & Age & Education & videos & videos & videos & Dropout \\
\toprule
 &            &          & \multicolumn{3}{c}{Survey Responses} & & & & & \multicolumn{3}{c}{Videos Watched} \\
 \cmidrule(r){4-6} \cmidrule(r){11-13}
 & Topic Area & Enrolled & Initial & Feedback & Both & Female & Age$^1$   & Education$^2$ & Dropout$^3$ & $>$ 30\% & $>$ 50\% & $>$ 80\% \\
\midrule
C1 & Business & 61,096   & 9,943  & 2,367    & 1,282    & 42\%   & 39 (30,49) & n.a.       & 10\% & 39\% & 20\% & 7\% \\
C2 & Business & 41,081   & 6,544  & 883      & 630      & 40\%   & 39 (30,49) & 97\%       & 9\%  & 32\% & 13\% & 2\% \\
C3 & CS       & 27,104   & 6,104 & 2,854     & 2,116    & 35\%   & 30 (22,41) & 74\%       & 2\%  & 67\% & 40\% & 7\% \\
C4 & CS       & 56,154   & 3,406 & 1,123     & 352      & 11\%   & 33 (27,42) & 91\%       & 21\% & 34\% & 16\% & 11\% \\
C5 & CS       & 57,636   & 5738  & 402       & 342      & 17\%   & 33 (26,43) & 91\%       & 14\% & 66\% & 55\% & 28\% \\
C6 & Engineering & 16,220 & 2,540 & 269      & 182      & 13\%   & 33 (27,45) & 92\%       & 15\% & 62\% & 49\% & 17\% \\
C7 & Enginerring & 7,178 & 1,312 & 202       & 167      & 12\%   & 27 (22,39) & 85\%       & 7\%  & 51\% & 18\% & 2\% \\
C8 & Humanities & 7,634 & 3,631  & 152       & 127      & 92\%   & 33 (26,45) & 93\%       & 7\%  & 45\% & 11\% & 0\% \\
C9 & Humanities & 6,475 & 3,315  & 326       & 262      & 90\%   & 32 (27,47) & 91\%       & 16\% & 69\% & 50\% & 17\% \\
C10 & Humanities & 9,903 & 4,227 & 1,570     & 1,066    & 52\%   & 39 (29,52) & 89\%       & 3\%  & 84\% & 74\% & 21\% \\
C11 & Humanities & 630 & 167     & 80        & 40       & 50\%   & 30 (27,40) & 97\%       & 16\% & 74\% & 55\% & 16\% \\
C12 & Math \& Stats & 49,317 & 3,090 & 862   & 510      & 33\%   & 41 (29,55) & 88\%       & 31\% & 27\% & 10\% & 1\% \\
C13 & Math \& Stats & 32,006 & 26,142 & 5,336 & 4,096   & 58\%   & 28 (16,46) & n.a.       & 4\%  & 69\% & 38\% & 8\% \\
C14 & Math \& Stats & 16,857 & 2,892 & 363   & 282      & 9\%    & 31 (26,38) & 99\%       & 14\% & 61\% & 45\% & 25\% \\
C15 & Math \& Stats & 37,017 & 11,629 & 1,854 & 1,521   & 20\%   & 35 (29,45) & 98\%       & 8\%  & 78\% & 67\% & 34\% \\
C16 & Math \& Stats & 27,236 & 2,711 & 637   & 610      & 82\%   & 43 (34,51) & n.a.       & 1\%  & 64\% & 36\% & 5\% \\
C17 & Math \& Stats & 13,132 & 3,629 & 843   & 626      & n.a.   & n.a.       & n.a.       & 5\%  & 70\% & 54\% & 14\% \\
\bottomrule
\multicolumn{13}{l}{$^1$ mean (upper, lower quartile)  $^2$ bachelors' or higher degree  $^3$ self-reported in the feedback survey}
\end{tabular}
\end{table*}
